Viscous Erosion in Porous Media

### 2018-01-18 docs/methods/erosion_methods.tex
Working on methods paper text.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{s:results}
With the description of the methods complete, we now present numerical results on bodies eroding in Stokes flow. We first discuss the case of a single eroding body, as certain features can be predicted analytically and thus used for validation. We then discuss the erosion of multiple bodies and highlight important differences that arise as compared to the single-body case.

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.85 \textwidth]{./figs/01bodseq.pdf}
\caption{A single body eroding in Stokes flow. As the body erodes, it develops a corner at its front and rear stagnation points, while remaining for-aft symmetric due to time-reversibility. Color indicates the vorticity of the surrounding flow, which, when evaluated on the boundary, gives the local shear stress. In this simulation, we use $N_\iin = 1024$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt = 1E-6$, and smoothing parameters of $\eps = 10/1024$ and $\sigma = 10/1024$. FYI, the body vanishes at time $t_{f} = 1.79E-2$.}
\label{01bodseq}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0

Figure \ref{01bodseq} shows the erosion of a single body, numerically simulated with $N_\iin = 1024$ discretization points. The figure shows the body at three evenly spaced times during the erosion process, with the color map to indicate the vorticity of the surrounding flow. When evaluated on the boundary, the vorticity is equivalent to shear stress and thus indicates the local erosion rate. As seen in the figure, the body is initially circular, with strongest vorticity above and below it. The flow is for-aft symmetric as a result of the time-reversibility of the Stokes equations, and vorticity vanishes at the body's front and rear stagnation points. At the next time step, the body has lost material due to erosion, but remains for-aft symmetric due to the flow symmetry. The greatest material loss has occurred at the body's top and bottom, where shear is strongest. Interestingly, the body has developed well-defined corners at its front and rear stagnation points. This geometric feature is a consequence of the erosion law, which depends on the {\em absolute} shear stress: wherever the stress vanishes, $\atau$ exhibits a corner, which manifests as a corner in the geometry. As shown in the third snapshot, this corner persists as the bodies becomes even more slender while vanishing.

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.80 \textwidth]{./figs/shrink_intface.pdf}
\caption{One body}
\label{shrink_intface}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0

To better understand the shape change, we show in Fig.~\ref{shrink_intface}(a) the interfaces of the body at several evenly spaced times. Here, color indicates time in relation to the time at which the body completely vanishes $t_{f} = 1.79E-2$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{s:results}
With the description of the methods complete, we now present numerical results on bodies eroding in Stokes flow. We first discuss the case of a single eroding body, as certain features can be predicted analytically and thus used for validation. We then discuss the erosion of multiple bodies and highlight important differences compared to the single-body case.

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.85 \textwidth]{./figs/01bodseq.pdf}
\caption{A single body eroding in Stokes flow. As the body erodes, it develops a corner at its front and rear stagnation points, while remaining for-aft symmetric due to time-reversibility. Color indicates the vorticity of the surrounding flow, which, when evaluated on the boundary, gives the local shear stress. In this simulation, we use $N_\iin = 1024$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt = 1E-6$, and smoothing parameters of $\eps = 10/1024$ and $\sigma = 10/1024$.}
\label{01bodseq}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0

Figure \ref{01bodseq} shows the erosion of a single body, numerically simulated with $N_\iin = 1024$ discretization points, and shown at three evenly spaced times. Here, color represents the vorticity of the surrounding flow, which, when evaluated on the boundary, indicates the shear stress and thus the local erosion rate. As seen in the left-most snapshot, the body is initially circular and has the strongest vorticity above and below it. The flow is for-aft symmetric as a result of the time-reversibility of the Stokes equations and vorticity vanishes at the body's front and rear stagnation points. At the next instance, the body has lost material due to erosion, but remains for-aft symmetric due to the flow symmetry. The greatest material loss has occurred at the body's top and bottom, where shear is strongest. Interestingly, the body has developed well-defined corners at its front and rear stagnation points. This geometric feature is a consequence of the erosion law, which depends on the {\em absolute} shear stress: wherever the stress vanishes, $\atau$ exhibits a corner, which manifests as a corner in the geometry. As shown in the third snapshot, this corner persists as the bodies becomes even more slender while wasting away. In this simulation, the body completely vanishes at a final time of $t_f = 1.79E-2$.

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.80 \textwidth]{./figs/shrink_intface.pdf}
\caption{Shape and stress evolution. (a) Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced time intervals. Color indicates normalized time, $t/t_f$, where $t_f = 1.79E-2$ is the time at which the body completely vanishes. (b) The distribution of absolute shear stress, $\atau$, along each of the interfaces. Initially the stress is distributed non-uniformly, but becomes more uniform 
}
\label{shrink_intface}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0

To better understand the body's shape evolution in this simulation, Fig.~\ref{shrink_intface}(a) shows several superimposed interfaces at evenly spaced times. The interfaces are color-coded by normalized time $t/t_f$. The body seems to converge to a shape that resembles an American football -- a fairly slender, for-aft symmetric shape with corners at the front and back. Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress, $\atau$, is distributed along each of these interfaces. The normalized arc length $s/L$ runs counterclockwise around the body, with $s/L = 0$ corresponding to the rear stagnation point and $s/L = 0.5$ the front stagnation point. At early times (yellow to orange), the stress is distributed non-uniformly, with highest values at the top and bottom of the body. As time proceeds, though, the stress becomes more evenly distributed along the body's surface (red). As the body nears the final stages of erosion (dark red), the stress actually becomes slightly higher near the stagnation points. A close look reveals that {\em at} the stagnation points, the stress always vanishes, though in a region that becomes increasingly narrow.
